Title

### 2014-07-18 paper.tex
describe the methods

Blah.

\subsection{Data Preparation}

@@

% quick structure
Each change includes a \emph{commit message}, which describes what is changed.
After a change is submitted to Gerrit, reviewers can give scores to it, which will decide if the change will be accepted or not.
Reviewers can also add comments to the change.
Comments may optionally be added to a specific line of code inside a changed file.

% conversion into vector, wow
The commit messages and all comment texts are converted into vectors as follows.
Firstly, we extracted words from the text, removed the stop words, and put the remaining words through Porter stemming algorithm.
Secondly, we combined all the remaining tokens to form a corpus of all words from all documents.
Finally, we used tf--idf to convert each document into a vector.

@@

\subsection{Model Generation}

% the metrics
For each comment, we computed a similarity and dissimilarity metrics
between the comment text and the corresponding commit message.
We chose cosine similarity and euclidean distance as the metrics to use in model generation.

% assumptions in categorization
The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also have tried using the `or' operator. We found that using `and' produces better result.}

% finding parameters
To find these parameters, we used a brute-force approach.

%€” Overview (No need for subsection)
%\subsection{Classifying useful discussion using text similarity and dissimilarity}
%Need a better section name - -.
%\subsection{Validation}
% (10-fold cross validation)
\section{Results}
\subsection{Studied Project and Data set}
\subsection{RQ1: Can we identify useful and useless discussion in code review?}
\subsection{RQ2: How impact of useless discussion impact to the software quality?}
\section{Threat to Validity}
\section{Conclusion and Future Work}

>>>>

Wow. This is just a placeholder text. Since this data is a great contribution to our research, I will cite their paper three times: [1][1][1].
TODO(get rid of this joke and this paragraph altogether, and replace with the actual overview of the method).

\subsection{The Data Set}

@@

% quick structure
Each change includes a \emph{commit message} which describes what is changed.
After a change is submitted to Gerrit, reviewers can give scores to it.
The scores will determine whether the change will be accepted or not.
Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.

\subsection{Data Preprocessing}

The commit messages and all comment texts are converted into vectors as part of the preprocessing step.
We wrote scripts in Ruby language to perform these tasks.

\subsubsection{Removal of automatically generated text}

First, all comments by the Gerrit system, \emph{Qt Sanity Bot}, and \emph{Qt Continuous Integration System} are skipped.

% conversion into vector, wow
Next, we looked for common patterns that appeared in the comments, because it is very likely that they are automatically generated.
This is accomplished by splitting texts into lines, and for each line, searching for words that can be found in the English wordlist\footnote{The wordlist found in \texttt{/usr/share/dict/words} from Ubuntu Linux distribution is used.}.
This effectively removed the ID numbers and other non-generic terms.

Next, the lines that appears most frequently are identified.
From these lines, we then constructed the regular expression patterns,
and finally, these patterns are used to filter out automatically generated text from our data.

\subsubsection{Stop word removal and stemming}

After the automatically generated messages are removed, we extracted the words by searching for alphanumeric characters and apostrophe, removed the stop words by using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}, and put the remaining words through Porter stemming algorithm.
The remaining words are then combined to form a corpus of all used words.

\subsubsection{Conversion into vector}

Finally, the tf--idf algorithm is used to convert each document into a vector.

@@

\subsection{Model Generation and Validation}

% the metrics
For each comment, we computed similarity and dissimilarity metrics
between the comment text and the corresponding commit message.
We chose cosine similarity and euclidean distance as the metrics to use in model generation.

% assumptions in categorization
The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also tried using the `or' operator, and found that using `and' produces better result.}

% finding parameters
To find these parameters, a brute-force approach is used.
This is possible because the set of $similarity$ and $distance$ values are discrete.
Each possible value of $A$, $B$, $C$, and $D$ are evaluated to find the constant that returns the maximum F$_1$ score.

% validation
To validate our model, 10-fold cross validation is used.
The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged.

\section{Results}

\subsection{Common Patterns}

The common patterns are found such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.

% corpus size and other statistics

\subsection{Studied Project and Data set}
\subsection{RQ1: Can we identify useful and useless discussion in code review?}
\subsection{RQ2: How impact of useless discussion impact to the software quality?}

\section{Discussion}

\section{Threat to Validity}

\section{Conclusion and Future Work}
